Notes of Quantum Field Theory in a Nutshell

### 2016-08-14 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update QFT in a nutshell.

\textbf{Unclear point}
Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
\ket{p}\bra{p} = 1$. What does it mean by saying
"to see that the normalization is correct" (pp. 10 and 11).
Why is effecting the Wick rotation is "somewhat rigorous"?

@@

\textbf{Unclear points}: I cannot follow all the calculation for 
$D(x)$, because my result is different from the book's. Also, the
physics picture about $D(x)$ on page 24, is badly reasoned. The
argument is tenuous, in my opinion.

@@

\paragraph{From particle to force}
With two delta source $J_a(x)=\delta^(3)(\vec{x}-\vec{x}_a)$, one can
describe two massive lumps setting on $\vec{x}_1$ and $\vec{x}_2$ and
not moving at all. These two lumps, coupled with the free field $\phi$,
will attract each other. To show the attraction, the author calculates
explicitly the $W(J)$, and identifies $iW(J) \equiv -iET$ (the
identification is substantiate by $e^{-iET} = Z = e^{iW(J)}$).
Finally, it shows:
\begin{align}
    E= -\frac{1}{4\pi r}e^{-mr}
\end{align}
This is actually the Yukawa model for the attraction between nucleons
in the atomic nucleus. A plot is in due:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/Yukawa-potential.pdf}
    \caption{Plot of Yukawa potential $-\frac{e^{-r}}{4 \pi  r}$}
\end{figure}

@@

\paragraph{Origin of force}
% TODO stops here.
\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\paragraph{Unclear point}
Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
\ket{p}\bra{p} = 1$. What does it mean by saying
"to see that the normalization is correct" (pp. 10 and 11).
Why is effecting the Wick rotation is "somewhat rigorous"?

@@

\paragraph{Unclear points}: I cannot follow all the calculation for 
$D(x)$, because my result is different from the book's. Also, the
physics picture about $D(x)$ on page 24, is badly reasoned. The
argument is tenuous, in my opinion.

@@

\paragraph{From particle to force}
With two delta source $J_a(x)=\delta^{(3)}(\vec{x}-\vec{x}_a)$, one can
describe two massive lumps setting on $\vec{x}_1$ and $\vec{x}_2$ and
not moving at all. These two lumps, coupled with the free field $\phi$,
will attract each other. To show the attraction, the author calculates
explicitly the $W(J)$\footnote{
    Specifically, he calculates the $J^*_1J_2$ and $J^*_2J_1$ terms,
    ignoring the $J^*_1J_1$ and $J^*_2J_2$ terms, because the latter
    appears in $W(J)$ regardless of the existance of the other particle.
}, and identifies $iW(J) \equiv -iET$ (the
identification is substantiate by $\braket{0|e^{-iET}|0} = Z = e^{iW(J)}$).
Finally, it shows:
\begin{align}
    E= -\frac{1}{4\pi r}e^{-mr}
\end{align}
This is actually the Yukawa model for the attraction between nucleons
in the atomic nucleus. A plot is in due:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/Yukawa-potential.pdf}
    \caption{Plot of Yukawa potential $-\frac{e^{-r}}{4 \pi  r}$}
\end{figure}

@@

\paragraph{Origin of force}
The energy calculated above, and the previous \textit{sink and source}
interpretation, lead us to believe that force is the result of an
exchange of particles.

\paragraph{Connected versus disconnected}
Here the author notes the Feynman's heuristic language to discribe
the integral related to $J(x)D(x-y)J(y)$ as a graph:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/J(x)D(x-y)J(y).png}
    \caption{$J(x)D(x-y)J(y)$}
\end{figure}
It also introduces the concept of connectedness or disconnectedness
in the graph (omitted here).

\paragraph{Unclear Points} Marked in the text.

\section{I.5 Coulomb an Newton: Repulsion and Attraction}
This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}

This clearly represent the idea of repulsive Coulomb force.
\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
